Machine Learning based TIR predictor - Methods

### 2020-05-14 main.tex
Updated results 140520

\begin{enumerate}
    \item 60 RBS sequences which are subsequent single nucleotide changes of all 20 nucleotides of the original, consensus sequence. This batch is designed to show us influence of such single nucleotide changes on the overall performance of the RBS and the potential impact of changes made beyond the core part.
    \item 30 RBS sequences fully and uniformly randomised (equal probability of choosing either nucleotide for each position) 
    \item 30 RBS sequences randomised based on the position probability matrix (PPM) \textcolor{red}{we need a citation and better explanation for this}  
    \item 60 RBS sequences recommended by initial machine learning approach. For this, and subsequent design rounds, we use bandit optimisation algorithm called Gaussian Process Upper Confidence Bound (GPUCB) (see \textbf{Methods} section) \cite{srinivas2012information}. Since we don't have access to any prior data fitting our design we approximated the recommendations based on the data from \textcite{jervis2018machine}. This data contains 113 non-repeated records for 56 unique RBS sequences with the respective TIR label. The label values are between 0 - 100,000 and skewed, which is shown in Figure xx. We have normalised the label to 0 - 1 using the min-max normalisation.   
\end{enumerate}{}

@@

\subsection{Initial predictions}

>>>>

\begin{enumerate}
    \item 60 RBS sequences which are subsequent single nucleotide changes of all 20 nucleotides of the original, consensus sequence. This batch is designed to show us influence of such single nucleotide changes on the overall performance of the RBS and the potential impact of changes made beyond the core part.
    \item 30 RBS sequences fully and uniformly randomised (equal probability of choosing either nucleotide for each position) 
    \item 30 RBS sequences randomised based on the position probability matrix (PPM) \textcolor{red}{we need a citation and better explanation for this}  
    \item 60 RBS sequences recommended by initial machine learning approach. For this, and subsequent design rounds, we use bandit optimisation algorithm called Gaussian Process Upper Confidence Bound (GPUCB) (see \textbf{Methods} section) \cite{srinivas2012information}. Since we don't have access to any prior data fitting our design we approximated the recommendations based on the data from \textcite{jervis2018machine}. 
\end{enumerate}{}

@@

\subsection{Initial bandit recommended designs}
As mentioned previously, for the first round of bandit-guided designs we used data-set available from \textcite{jervis2018machine}. This set contains 113 non-repeated records for 56 unique RBS sequences with the respective TIR label. The label values are between 0 - 100,000 and skewed, which is shown in Figure xx. We have normalised the label to 0 - 1 using the min-max normalisation.

### 2020-05-14 methods.tex
Updated results 140520

\begin{itemize}
    \item \textit{Gaussian process regression (GPR)}. We model $f$ as a sample from a \textit{Gaussian process} $GP(\mu(\mathbf{x}), k(\mathbf{x}, \mathbf{x'}))$, which is specified by the mean function $\mu(\mathbf{x})=\mathbb{E}[f(\mathbf{x})]$ and the kernel (or covariance) function $k\left(\mathbf{x}, \mathbf{x}^{\prime}\right)=\mathbb{E}[(f(\mathbf{x})-\left.\mu(\mathbf{x}))\left(f\left(\mathbf{x}^{\prime}\right)-\mu\left(\mathbf{x}^{\prime}\right)\right)\right]$. We will introduce the kernel function we choose in the below. 
    A Gaussian process regression model \cite{Rasmussen2004},

    \item \textit{Upper confidence bound (UCB)}. recommends sequences to test for next round.
\end{itemize}

>>>>

\begin{itemize}
    \item \textit{Gaussian process regression (GPR)}.
    A Gaussian process regression model \cite{Rasmussen2004} is a Bayesian approach to regression which provide uncertainty measurements on predictions. 
    We model $f$ as a sample from a \textit{Gaussian process} $GP(\mu(\mathbf{x}), k(\mathbf{x}, \mathbf{x'}))$, which is specified by the mean function $\mu(\mathbf{x})=\mathbb{E}[f(\mathbf{x})]$ and the kernel (or covariance) function $k\left(\mathbf{x}, \mathbf{x}^{\prime}\right)=\mathbb{E}[(f(\mathbf{x})-\left.\mu(\mathbf{x}))\left(f\left(\mathbf{x}^{\prime}\right)-\mu\left(\mathbf{x}^{\prime}\right)\right)\right]$. We will introduce the kernel function we choose in the below.

    \item \textit{Upper confidence bound (UCB)}. Bandit algorithms \cite{lattimore2018bandit} provide various approaches to sequentially design an where an agent adaptively chooses one or more options among several actions based on certain policies. We consider a type of bandit algorithms, the upper confidence bound algorithm, which is based on the \textit{optimism in the face of uncertainty}. The UCB algorithm, as the name suggested, basically selects RBS sequences with the maximum upper confidence bound, i.e. $\operatorname{argmax}_{\mathbf{x_i \in \mathcal{D}}} \left( \mu_t(\mathbf{x_i}) + \beta_t \sigma_t(\mathbf{x_i})\right)$, where $\beta_T$ is a hyperparmeter balancing the exploitation and exploration, $\mu_t(\mathbf{x}_i), \sigma_t(\matbf{x}_i)$ are the predicted mean and standard deviation at round $t$ for the sequence $\mathbf{x}_i$. 
\end{itemize}
